\thetitle

### 2022-04-18 paper/paper.tex
plot of simulated annealing grid search, update accuracy plot, translate writeup

\usepackage{hyperref}
\hyperbaseurl{}
\urlstyle{same}
\usepackage[ruled,linesnumbered]{algorithm2e}
\newcommand{\lIfElse}[3]{\lIf{#1}{#2 \textbf{else}~#3}}

@@

% Language selector
\newif\ifen
\entrue % Change to false to export Korean

@@

\begin{abstract}
This paper considers the maximization of the expected maximum value of a portfolio of random variables subject to a budget constraint. We refer to this as the optimal college application problem. When each variable's cost, or each college's application fee, is identical, we show that the optimal portfolios are nested in the budget constraint, yielding an exact polynomial-time algorithm. When colleges differ in their application fees, we show that the problem is NP-complete. We provide three algorithms for this more general setup. The first is a branch-and-bound routine. The second is an dynamic program that produces an exact solution in pseudopolynomial time. The third is a different dynamic program that yields fully polynomial-time approximation scheme. Numerical experiments demonstrate the algorithms' practicality.

@@

\ifen
We refer to the set $\mathcal{X} \subseteq \mathcal{C}$ of schools to which a student applies as her \emph{application portfolio.} The expected utility the student receives from $\mathcal{X}$ is called its \emph{valuation}. %Let $x$ denote the same encoded as a binary vector, where $x_j=1 \iff j\in \mathcal{X}$ for $j=1\dots m$.
\else
학생이 지원하는 학교 집합 $\mathcal{X} \subseteq \mathcal{C}$를 `지원 포트폴리오'라고 부르자. $\mathcal{X}$에서 학생이 받는 기대 효용을 포트폴리오의 `가치'라고 한다.
\fi 
\begin{definition}[\ifen Portfolio valuation function\else 포트폴리오 가치 함수\fi]
$v(\mathcal{X}) =  \operatorname{E}\left[\max\bigr\{t_0,
\max\{t_j Z_j : j \in \mathcal{X}\}\bigr\}\right]$.
\end{definition}
\ifen
It is helpful to define the random variable $X  = \max\{ t_j Z_j : j \in \mathcal{X}\}$ as the utility achieved by the schools in the portfolio, so that when $t_0 = 0$, $v(\mathcal{X}) = \operatorname{E}[X]$. Similar pairs of variables with script and italic names such as $\mathcal{Y}_h$ and $Y_h$ carry an analogous meaning.
\else
편의상 포트폴리오에 속한 학교가 실제로 이루는 효용을 확률 변수 $X  = \max\{ t_j Z_j : j \in \mathcal{X}\}$로 정의한다. 그러면 $t_0 = 0$이면 $v(\mathcal{X}) = \operatorname{E}[X]$임을 알 수 있다. 비슷한 식으로 $\mathcal{Y}_h$와 $Y_h$ 같은 스크립트체와 이탈릭체로 표기한 변수 쌍은 유사한 의미를 가진다.
\fi

@@

\ifen {
\begin{algorithm}[h] 
%\DontPrintSemicolon
\caption{Optimal portfolio algorithm for Alma’s problem.} \label{algorithmforlargeh}
\KwData{Utility values $t \in(0, \infty)^m$, admissions probabilities $f \in (0, 1]^m$, application limit $h \leq m$.}
%Index schools in ascending order by $t$\;
$\mathcal{C} \gets \{1 \dots m\}$\;
$\mathtt{X, V} \gets $ empty lists\;
\For{$i=1\dots h$}
{
    $k \gets \argmax_{j \in \mathcal{C}}\{f_j t_j\}$\;
    $\mathcal{C} \gets \mathcal{C} \setminus \{k\}$\;
    $\operatorname{append!}(\mathtt{X}, k)$\;
     \lIfElse{$i=1$}{$\operatorname{append!}(\mathtt{V}, f_k t_k)$}
     {$\operatorname{append!}(\mathtt{V}, \mathtt{V[i-1]} + f_k t_k)$}
    \For{$j \in \mathcal{C}$}
	{
	\lIfElse{$t_j \leq t_k$}{$t_j \gets (1 -  f_k) t_j $}{$t_j \gets  t_j -  f_k t_k$}
	}
}
\Return{$\mathtt{X, V}$}
\end{algorithm}
} \else {
\begin{algorithm}[H] 
%\DontPrintSemicolon
\caption{알마의 문제를 위한 최적 포트폴리오 알고리즘.} \label{algorithmforlargeh}
\KwData{효용 모수 $t \in(0, \infty)^m$, 합격 확률 $f \in (0, 1]^m$, 지원 제한 $h \leq m$.}
%$t$의 순서대로 학교의 지표를 짓는다\;
$\mathcal{C} \gets \{1 \dots m\}$\;
$\mathtt{X, V} \gets $ 빈 목록\;
\For{$i=1\dots h$}
{
    $k \gets \argmax_{j \in \mathcal{C}}\{f_j t_j\}$\;
    $\mathcal{C} \gets \mathcal{C} \setminus \{k\}$\;
    $\operatorname{append!}(\mathtt{X}, k)$\;
     \lIfElse{$i=1$}{$\operatorname{append!}(\mathtt{V}, f_k t_k)$}
     {$\operatorname{append!}(\mathtt{V}, \mathtt{V[i-1]} + f_k t_k)$}
    \For{$j \in \mathcal{C}$} 
	{
	\lIfElse{$t_j \leq t_k$}{$t_j \gets (1 -  f_k) t_j $}{$t_j \gets  t_j -  f_k t_k$}
	}
}
\Return{$\mathtt{X, V}$}
\end{algorithm}
} \fi

@@

\ifen
\noindent In this section, we show that this problem is NP-complete, then provide three algorithmic solutions: an exact branch-and-bound routine, an exact dynamic program, and a fully polynomial-time approximation scheme (FPTAS).
\else
\noindent 본 절에서 이 문제가 NP-complete함을 보이고 3가지 해법을 제시한다: 정확한 분지한계법 해법, 정확한 동적 계획 해법, 그리고 완전 다항 시간 근사 해법 (fully polynomial-time approximation scheme, FPTAS).
\fi

@@

\ifen 
An intuitive extension of the greedy algorithm for Alma's problem is to iteratively add to $\mathcal{X}$ the school $k$ for which $\bigl( v(\mathcal{X}\cup\{k\}) - v(\mathcal{X}) \bigr) / g_k$ is largest. However, the construction above shows that the objective function of Ellis's problem can approximate that of a knapsack problem with arbitrary precision. Therefore, in pathological examples such as the following, the greedy algorithm can achieve an arbitrarily small approximation ratio. 
\else
알마 문제를 위한 탐욕 해법의 직관적인 확장은 $\bigl( v(\mathcal{X}\cup\{k\}) - v(\mathcal{X}) \bigr) / g_k$-값이 가장 큰 학교 $k$를  $\mathcal{X}$에 차례대로 추가하는 것이다. 그러나 위에서 도출한 변환은 엘리스 문제의 목적함수를 배낭 문제의 목적함수의 원하는 만큼 정확한 근사로 만들 수 있음을 의미한다. 따라서 다음 같은 병례에서 탐욕 해법은 임의로 낮은 근사 비율을 일으킬 수 있다.
\fi
\begin{example}
\ifen
Let $t = (10, 2021)$, $f = (1, 1)$, $g = (1, 500)$, and $H = 500$. Then the greedy approximation algorithm produces the clearly inoptimal solution $\mathcal{X} = \{1\}$. 
\else
 $t = (10, 2021)$, $f = (1, 1)$, $g = (1, 500)$, 그리고 $H = 500$이라고 하자. 그러면 탐욕 해법은 $\mathcal{X} = \{1\}$을 출력하며 이는 분명히 최적해가 아니다.
\fi
\end{example} 
\ifen
We might expect to obtain a better approximate solution to Ellis's problem by solving the following knapsack problem (nevermind that it is NP-complete) as a surrogate.
\begin{equation}
\text{maximize}\quad \sum_{j \in \mathcal{X}} f_j t_j \qquad \text{subject to}\quad\mathcal{X}\subseteq\mathcal{C},~~\sum_{j \in \mathcal{X}} g_j \leq H
\end{equation}
However, upon inspection, this solution merely generalizes the na\"ive algorithm for Alma's problem (Definition \ref{naivealgorithm}). In Ellis's problem, because the number of schools in the optimal portfolio can be as large as $m-1$, the knapsack solution's approximation coefficient is $1/(m-1)$ by analogy with \eqref{oneoverhopt}. A tight example is as follows. 
\else
엘리스 문제의 좀 더 좋은 근사해를 찾기 위해 다음 배낭 문제를 (NP-complete함을 무시하고) 대리 문제로 푸는 것에 매력은 있다.
\begin{equation}
\text{maximize}\quad \sum_{j \in \mathcal{X}} f_j t_j \qquad \text{subject to}\quad\mathcal{X}\subseteq\mathcal{C},~~\sum_{j \in \mathcal{X}} g_j \leq H
\end{equation}
그러나 이러한 해법은 사실 알마 문제의 나이브 해법(정의 \ref{naivealgorithm})의 단순한 일반화임을 알 수 있다. 엘리스 문제에서 최적 포트폴리오에 크기가 $m-1$이 될 수 있으므로 배낭 문제 해법의 근사 계수는 \eqref{oneoverhopt}과(와) 유사하듯이 $1 / (m-1)$이다. 타이트한 예는 다음과 같다.
\fi
\begin{example} \label{knapsackheuristicellis}
\ifen Consider the following instance of Ellis's problem, where $H = m-1$.
\else 엘리스 문제의 다음 인스턴스를 고려하자. 단, $H = m-1$이다. \fi
\begin{center}
\begin{tabular}{r|cccc}
$j$   & $1$            & $\cdots$ & $m-1$          & $m$            \\ \hline
$f_j$ & $1$            &  $\cdots$ & $1$            & $\frac{1}{m-1}$ \\
$t_j$ & $\frac{1}{m-1}$ &  $\cdots$ & $\frac{1}{m-1}$ & $m-1$          \\
$g_j$ & $1$            &  $\cdots$ & $1$            & $m-1$         
\end{tabular}%
\end{center}
\ifen
The feasible solutions $\mathcal{Y} = \{1, \dots, m-1\}$ and $\mathcal{X} = \{ m\}$ each have $\sum_{j \in \mathcal{Y}} f_j t_j = \sum_{j \in \mathcal{X}} f_j t_j =  1$, and thus the knapsack algorithm can choose $\mathcal{Y}$ with $v(\mathcal{Y}) = 1/(m-1)$. But the optimal solution is  $\mathcal{X}$ with $v(\mathcal{X}) =  1$. 
\else
가능해 $\mathcal{Y} = \{1, \dots, m-1\}$와 $\mathcal{X} = \{ m\}$에 대해 $\sum_{j \in \mathcal{Y}} f_j t_j = \sum_{j \in \mathcal{X}} f_j t_j =  1$이므로 배낭 문제 해법은  $\mathcal{Y}$를 선택할 수 있다. 그의 가치는 $v(\mathcal{Y}) = 1/(m-1)$이다. 그러나 $\mathcal{X}$는 최적해이며 그의 가치는 $v(\mathcal{X}) =  1$이다.
\fi
\end{example}

\ifen 
\noindent In summary, neither a greedy algorithm nor a knapsack-based algorithm solves Ellis's problem to optimality. 
\else
\noindent 탐욕 해법 또는 배낭 문제 기반 해법으로 엘리스 문제의 정확한 최적해를 구할 수 없음을 의미한다.
\fi

@@

\ifen {
\begin{algorithm}[h] 
%\DontPrintSemicolon
\caption{Branch and bound for Ellis's problem.} \label{ellisbnb}
\KwData{Utility values $t \in(0, \infty)^m$, admissions probabilities $f \in (0, 1]^m$, application costs $g \in (0, \infty)^m$, budget $H \in (0, \infty)$.}
Root node $n_0 \gets (\O, \O, \mathcal{C})$\;
Current lower bound $L \gets 0$ and best solution $\mathcal{X} \gets \O$\;
Candidate set $\mathfrak{T} \gets \{ n_0\}$\;
\While{not finished}{
	\lIf{$\mathfrak{T} = \O$}{\Return{$\mathcal{X}, L$}}
	\Else{
		$n \gets \argmax\{ v_{\mathrm{LP}}^*[n] : n \in \mathfrak{T}\}$\;
		Remove $n$ from $\mathfrak{T}$\;
%		Generate children of $n$\;
		\For{each child $n'$ of $n$}{
			\If{$L < v_{\mathcal{I}}[n']$}{
				$L \gets v_{\mathcal{I}}[n']$\;
				Update $\mathcal{X}$ to the $\mathcal{I}$-set associated with $n'$\;
			}
			\lIf{$v_{\mathrm{LP}}^*[n] > L$ and $n'$ is not a leaf}{add $n'$ to $\mathfrak{T}$}
		}
		\For{$n'' \in \mathfrak{T}$} {
			\lIf{$L >  v_{\mathrm{LP}}^*[n'']$}{remove $n''$ from $\mathfrak{T}$}
		}
	}
}
\end{algorithm}
} \else {
\begin{algorithm}[h] 
%\DontPrintSemicolon
\caption{엘리스의 문제를 위한 분지한계법.} \label{ellisbnb}
\KwData{효용 모수 $t \in(0, \infty)^m$, 합격 확률 $f \in (0, 1]^m$, 지원 비용 $g \in (0, \infty)^m$, 예산 $H \in (0, \infty)$.}
뿌리 마디 $n_0 \gets (\O, \O, \mathcal{C})$\;
현재 하한 $L \gets 0$ 및 최적해 $\mathcal{X} \gets \O$\;
후보 집합 $\mathfrak{T} \gets \{ n_0\}$\;
\While{종료되지 않음}{
	\lIf{$\mathfrak{T} = \O$}{\Return{$\mathcal{X}, L$}}
	\Else{
		$n \gets \argmax\{ v_{\mathrm{LP}}^*[n] : n \in \mathfrak{T}\}$\;
		$\mathfrak{T}$에서 $n$을 제거한다\;
%		Generate children of $n$\;
		\For{$n$의 각 새끼 마디 $n'$}{
			\If{$L < v_{\mathcal{I}}[n']$}{
				$L \gets v_{\mathcal{I}}[n']$\;
				$\mathcal{X}$을 $n'$에 대응하는 $\mathcal{I}$-집합으로 수정한다\;
			}
			\lIf{$v_{\mathrm{LP}}^*[n] > L$이고 $n'$이 잎 마디 아님}{$\mathfrak{T}$에 $n'$을 추가한다}
		}
		\For{$n'' \in \mathfrak{T}$} {
			\lIf{$L >  v_{\mathrm{LP}}^*[n'']$}{$\mathfrak{T}$에서 $n''$을 제거한다}
		}
	}
}
\end{algorithm}
} \fi

@@

\ifen {
\begin{algorithm}[h] 
%\DontPrintSemicolon
\caption{Dynamic program for Ellis's problem with integral application costs.} \label{ellisDP1}
\KwData{Utility values $t \in(0, \infty)^m$, admissions probabilities $f \in (0, 1]^m$, application costs $g \in \mathbb{N}^m$, budget $H \in\mathbb{N}$.}
Index schools in ascending order by $t$\;
%\SetKwProg{Fn}{function}{ do}{end}
%\Fn{$V(j, h)$}{
%	\lIf{$h < g_j$}{\Return{$-\infty$}}
%	\lElseIf{$j = 0$ or $h=0$}{\Return{$0$}}
%	\lElse{\Return{$\max\bigl\{ V(j-1, h), (1 - f_j) V(j-1, h-g_j) + f_j t_j \bigr\}$}}
%}
Fill a lookup table with the values of $V[j, h]$\; \label{Vcreatedlookuptable}
$h \gets H$\;
$\mathcal{X} \gets \O$\;
\For{$j = m, m-1, \dots, 1$}{
	\If{$V[j-1, h] < V[j, h]$}{
		$\mathcal{X} \gets \mathcal{X}\cup\{j\}$\; 
		$h \gets h - g_j$\;
	}
}
\Return{$\mathcal{X}$}
\end{algorithm}
} \else {
\begin{algorithm}[h] 
%\DontPrintSemicolon
\caption{정수 지원 비용의 엘리스 문제를 위한 동적 계획 해법.} \label{ellisDP1}
\KwData{효용 모수 $t \in(0, \infty)^m$, 합격 확률 $f \in (0, 1]^m$, 지원 비용 $g \in \mathbb{N}^m$, 예산 $H \in\mathbb{N}$.}
$t$의 순서대로 학교를 배열한다\;
%\SetKwProg{Fn}{function}{ do}{end}
%\Fn{$V(j, h)$}{
%	\lIf{$h < g_j$}{\Return{$-\infty$}}
%	\lElseIf{$j = 0$ or $h=0$}{\Return{$0$}}
%	\lElse{\Return{$\max\bigl\{ V(j-1, h), (1 - f_j) V(j-1, h-g_j) + f_j t_j \bigr\}$}}
%}
$V[j, h]$의 값으로 표를 채운다\; \label{Vcreatedlookuptable}
$h \gets H$\;
$\mathcal{X} \gets \O$\;
\For{$j = m, m-1, \dots, 1$}{
	\If{$V[j-1, h] < V[j, h]$}{
		$\mathcal{X} \gets \mathcal{X}\cup\{j\}$\; 
		$h \gets h - g_j$\;
	}
}
\Return{$\mathcal{X}$}
\end{algorithm}
}\fi

@@

\ifen \subsection{Simulated annealing} \else \subsection{Simulated annealing}\fi\label{numericalexperiments}
Simulated annealing is a popular local-search technique for nonconvex optimization problems. Because of their inherent randomness, simulated-annealing algorithms offer no accuracy guarantee; however, they are easy to implement, computationally inexpensive, and often produce solutions with a small optimality gap. In this section, we present a simulated-annealing algorithm for Ellis's problem. It is based on the procedure for integer programs outlined by Wolsey (1998, \S\,12.3.2)

>>>>

\usepackage{hyperref}
\hyperbaseurl{}
\urlstyle{same}
\usepackage[ruled,linesnumbered]{algorithm2e}
\newcommand{\lIfElse}[3]{\lIf{#1}{#2 \textbf{else}~#3}}
\SetKwInOut{KwParams}{Parameters}

@@

% Language selector
\newif\ifen
\enfalse% Change to false to export Korean

@@

\begin{abstract}
This paper considers the maximization of the expected maximum value of a portfolio of random variables subject to a budget constraint. We refer to this as the optimal college application problem. When each variable's cost, or each college's application fee, is identical, we show that the optimal portfolios are nested in the budget constraint, yielding an exact polynomial-time algorithm. When colleges differ in their application fees, we show that the problem is NP-complete. We provide three algorithms for this more general setup. The first is a branch-and-bound routine. The second is an dynamic program that produces an exact solution in pseudopolynomial time. The third is a different dynamic program that yields a fully polynomial-time approximation scheme. Numerical experiments demonstrate the algorithms' practicality.

@@

\ifen
We refer to the set $\mathcal{X} \subseteq \mathcal{C}$ of schools to which a student applies as her \emph{application portfolio.} The expected utility the student receives from $\mathcal{X}$ is called its \emph{valuation}. %Let $x$ denote the same encoded as a binary vector, where $x_j=1 \iff j\in \mathcal{X}$ for $j=1\dots m$.
\else
학생이 지원하는 학교 집합 $\mathcal{X} \subseteq \mathcal{C}$를 `지원 포트폴리오'라고 부르자. $\mathcal{X}$에서 학생이 받는 기대 효용을 포트폴리오의 `가치'라고 한다.
\fi 
\begin{definition}[\ifen Portfolio valuation function\else 포트폴리오 가치 함수\fi]
$v(\mathcal{X}) =  \operatorname{E}\left[\max\bigr\{t_0,
\max\{t_j Z_j : j \in \mathcal{X}\}\bigr\}\right]$.
\end{definition}
\ifen
\noindent It is helpful to define the random variable $X  = \max\{ t_j Z_j : j \in \mathcal{X}\}$ as the utility achieved by the schools in the portfolio, so that when $t_0 = 0$, $v(\mathcal{X}) = \operatorname{E}[X]$. Similar pairs of variables with script and italic names such as $\mathcal{Y}_h$ and $Y_h$ will carry an analogous meaning.
\else
\noindent 편의상 포트폴리오에 속한 학교가 실제로 이루는 효용을 확률 변수 $X  = \max\{ t_j Z_j : j \in \mathcal{X}\}$로 정의한다. 그러면 $t_0 = 0$이면 $v(\mathcal{X}) = \operatorname{E}[X]$임을 알 수 있다. 비슷한 식으로 $\mathcal{Y}_h$와 $Y_h$ 같은 스크립트체와 이탈릭체로 표기한 변수 쌍은 유사한 의미를 가진다.
\fi

@@

\ifen {
\begin{algorithm}[h] 
%\DontPrintSemicolon
\caption{Optimal portfolio algorithm for Alma’s problem.} \label{algorithmforlargeh}
\KwIn{Utility values $t \in(0, \infty)^m$, admissions probabilities $f \in (0, 1]^m$, application limit $h \leq m$.}
%Index schools in ascending order by $t$\;
$\mathcal{C} \gets \{1 \dots m\}$\;
$\mathtt{X, V} \gets $ empty lists\;
\For{$i=1\dots h$}
{
    $k \gets \argmax_{j \in \mathcal{C}}\{f_j t_j\}$\;
    $\mathcal{C} \gets \mathcal{C} \setminus \{k\}$\;
    $\operatorname{append!}(\mathtt{X}, k)$\;
     \lIfElse{$i=1$}{$\operatorname{append!}(\mathtt{V}, f_k t_k)$}
     {$\operatorname{append!}(\mathtt{V}, \mathtt{V[i-1]} + f_k t_k)$}
    \For{$j \in \mathcal{C}$}
	{
	\lIfElse{$t_j \leq t_k$}{$t_j \gets (1 -  f_k) t_j $}{$t_j \gets  t_j -  f_k t_k$}
	}
}
\Return{$\mathtt{X, V}$}
\end{algorithm}
} \else {
\begin{algorithm}[H] 
%\DontPrintSemicolon
\caption{알마의 문제를 위한 최적 포트폴리오 알고리즘.} \label{algorithmforlargeh}
\KwIn{효용 모수 $t \in(0, \infty)^m$, 합격 확률 $f \in (0, 1]^m$, 지원 제한 $h \leq m$.}
%$t$의 순서대로 학교의 지표를 짓는다\;
$\mathcal{C} \gets \{1 \dots m\}$\;
$\mathtt{X, V} \gets $ 빈 목록\;
\For{$i=1\dots h$}
{
    $k \gets \argmax_{j \in \mathcal{C}}\{f_j t_j\}$\;
    $\mathcal{C} \gets \mathcal{C} \setminus \{k\}$\;
    $\operatorname{append!}(\mathtt{X}, k)$\;
     \lIfElse{$i=1$}{$\operatorname{append!}(\mathtt{V}, f_k t_k)$}
     {$\operatorname{append!}(\mathtt{V}, \mathtt{V[i-1]} + f_k t_k)$}
    \For{$j \in \mathcal{C}$} 
	{
	\lIfElse{$t_j \leq t_k$}{$t_j \gets (1 -  f_k) t_j $}{$t_j \gets  t_j -  f_k t_k$}
	}
}
\Return{$\mathtt{X, V}$}
\end{algorithm}
} \fi

@@

\ifen
\noindent In this section, we show that this problem is NP-complete, then provide four algorithmic solutions: an exact branch-and-bound routine, an exact dynamic program, a fully polynomial-time approximation scheme (FPTAS), and a simulated-annealing heuristic. 
\else
\noindent 본 절에서 이 문제가 NP-complete함을 보이고 3가지 해법을 제시한다: 정확한 분지한계법 해법, 정확한 동적 계획 해법, 완전 다항 시간 근사 해법(fully polynomial-time approximation scheme, FPTAS), 그리고 모의 담금질(simulated annealing) 휴리스틱.
\fi

@@

\ifen 
An intuitive extension of the greedy algorithm for Alma's problem is to iteratively add to $\mathcal{X}$ the school $k$ for which $\bigl( v(\mathcal{X}\cup\{k\}) - v(\mathcal{X}) \bigr) / g_k$ is largest. But the construction above shows that the objective function of Ellis's problem can approximate that of a knapsack problem with arbitrary precision. Therefore, in pathological examples such as the following, the greedy algorithm can achieve an arbitrarily small approximation ratio. 
\else
알마 문제를 위한 탐욕 해법의 직관적인 확장은 $\bigl( v(\mathcal{X}\cup\{k\}) - v(\mathcal{X}) \bigr) / g_k$-값이 가장 큰 학교 $k$를  $\mathcal{X}$에 차례대로 추가하는 것이다. 그러나 위에서 도출한 변환은 엘리스 문제의 목적함수를 배낭 문제의 목적함수의 원하는 만큼 정확한 근사로 만들 수 있음을 의미한다. 따라서 다음 같은 병례에서 탐욕 해법은 임의로 낮은 근사 비율을 일으킬 수 있다.
\fi
\begin{example} \label{greedyzeroellis}
\ifen
Let $t = (10, 2021)$, $f = (0.1, 0.1)$, $g = (1, 500)$, and $H = 500$. Then the greedy approximation algorithm produces the clearly inoptimal solution $\mathcal{X} = \{1\}$. 
\else
 $t = (10, 2021)$, $f = (0.1, 0.1)$, $g = (1, 500)$, 그리고 $H = 500$이라고 하자. 그러면 탐욕 해법은 $\mathcal{X} = \{1\}$을 출력하며 이는 분명히 최적해가 아니다.
\fi
\end{example} 
\ifen
We might expect to obtain a better approximate solution to Ellis's problem by solving the following knapsack problem (nevermind that it is NP-complete) as a surrogate.
\begin{equation}
\text{maximize}\quad \sum_{j \in \mathcal{X}} f_j t_j \qquad \text{subject to}\quad\mathcal{X}\subseteq\mathcal{C},~~\sum_{j \in \mathcal{X}} g_j \leq H
\end{equation}
However, upon inspection, this solution merely generalizes the na\"ive algorithm for Alma's problem (Definition \ref{naivealgorithm}). In Ellis's problem, because the number of schools in the optimal portfolio can be as large as $m-1$, the knapsack solution's approximation coefficient is $1/(m-1)$ by analogy with \eqref{oneoverhopt}. A tight example is as follows. 
\else
엘리스 문제의 좀 더 좋은 근사해를 찾기 위해 다음 배낭 문제를 (NP-complete함을 무시하고) 대리 문제로 푸는 것에 매력은 있다.
\begin{equation}
\text{maximize}\quad \sum_{j \in \mathcal{X}} f_j t_j \qquad \text{subject to}\quad\mathcal{X}\subseteq\mathcal{C},~~\sum_{j \in \mathcal{X}} g_j \leq H
\end{equation}
그러나 이러한 해법은 사실 알마 문제의 나이브 해법(정의 \ref{naivealgorithm})의 단순한 일반화임을 알 수 있다. 엘리스 문제에서 최적 포트폴리오에 크기가 $m-1$이 될 수 있으므로 배낭 문제 해법의 근사 계수는 \eqref{oneoverhopt}과(와) 유사하듯이 $1 / (m-1)$이다. 타이트한 예는 다음과 같다.
\fi
\begin{example} \label{knapsackheuristicellis}
\ifen Consider the following instance of Ellis's problem, where $H = m-1$.
\else 엘리스 문제의 다음 인스턴스를 고려하자. 단, $H = m-1$이다. \fi
\begin{center}
\begin{tabular}{r|cccc}
$j$   & $1$            & $\cdots$ & $m-1$          & $m$            \\ \hline
$f_j$ & $1$            &  $\cdots$ & $1$            & $\frac{1}{m-1}$ \\
$t_j$ & $\frac{1}{m-1}$ &  $\cdots$ & $\frac{1}{m-1}$ & $m-1$          \\
$g_j$ & $1$            &  $\cdots$ & $1$            & $m-1$         
\end{tabular}%
\end{center}
\ifen
The feasible solutions $\mathcal{Y} = \{1, \dots, m-1\}$ and $\mathcal{X} = \{ m\}$ each have $\sum_{j \in \mathcal{Y}} f_j t_j = \sum_{j \in \mathcal{X}} f_j t_j =  1$, and thus the knapsack algorithm can choose $\mathcal{Y}$ with $v(\mathcal{Y}) = 1/(m-1)$. But the optimal solution is  $\mathcal{X}$ with $v(\mathcal{X}) =  1$. 
\else
가능해 $\mathcal{Y} = \{1, \dots, m-1\}$와 $\mathcal{X} = \{ m\}$에 대해 $\sum_{j \in \mathcal{Y}} f_j t_j = \sum_{j \in \mathcal{X}} f_j t_j =  1$이므로 배낭 문제 해법은  $\mathcal{Y}$를 선택할 수 있다. 그의 가치는 $v(\mathcal{Y}) = 1/(m-1)$이다. 그러나 $\mathcal{X}$는 최적해이며 그의 가치는 $v(\mathcal{X}) =  1$이다.
\fi
\end{example}

\ifen 
In summary, neither a greedy algorithm nor a knapsack-based algorithm solves Ellis's problem to optimality. 
\else
탐욕 해법 또는 배낭 문제 기반 해법으로 엘리스 문제의 정확한 최적해를 구할 수 없음을 의미한다.
\fi

@@

\ifen {
\begin{algorithm}[h] 
%\DontPrintSemicolon
\caption{Branch and bound for Ellis's problem.} \label{ellisbnb}
\KwIn{Utility values $t \in(0, \infty)^m$, admissions probabilities $f \in (0, 1]^m$, application costs $g \in (0, \infty)^m$, budget $H \in (0, \infty)$.}
Root node $n_0 \gets (\O, \O, \mathcal{C})$\;
Current lower bound $L \gets 0$ and best solution $\mathcal{X} \gets \O$\;
Candidate set $\mathfrak{T} \gets \{ n_0\}$\;
\While{not finished}{
	\lIf{$\mathfrak{T} = \O$}{\Return{$\mathcal{X}, L$}}
	\Else{
		$n \gets \argmax\{ v_{\mathrm{LP}}^*[n] : n \in \mathfrak{T}\}$\;
		Remove $n$ from $\mathfrak{T}$\;
%		Generate children of $n$\;
		\For{each child $n'$ of $n$}{
			\If{$L < v_{\mathcal{I}}[n']$}{
				$L \gets v_{\mathcal{I}}[n']$\;
				Update $\mathcal{X}$ to the $\mathcal{I}$-set associated with $n'$\;
			}
			\lIf{$v_{\mathrm{LP}}^*[n] > L$ and $n'$ is not a leaf}{add $n'$ to $\mathfrak{T}$}
		}
		\For{$n'' \in \mathfrak{T}$} {
			\lIf{$L >  v_{\mathrm{LP}}^*[n'']$}{remove $n''$ from $\mathfrak{T}$}
		}
	}
}
\end{algorithm}
} \else {
\begin{algorithm}[h] 
%\DontPrintSemicolon
\caption{엘리스의 문제를 위한 분지한계법.} \label{ellisbnb}
\KwIn{효용 모수 $t \in(0, \infty)^m$, 합격 확률 $f \in (0, 1]^m$, 지원 비용 $g \in (0, \infty)^m$, 예산 $H \in (0, \infty)$.}
뿌리 마디 $n_0 \gets (\O, \O, \mathcal{C})$\;
현재 하한 $L \gets 0$ 및 최적해 $\mathcal{X} \gets \O$\;
후보 집합 $\mathfrak{T} \gets \{ n_0\}$\;
\While{종료되지 않음}{
	\lIf{$\mathfrak{T} = \O$}{\Return{$\mathcal{X}, L$}}
	\Else{
		$n \gets \argmax\{ v_{\mathrm{LP}}^*[n] : n \in \mathfrak{T}\}$\;
		$\mathfrak{T}$에서 $n$을 제거\;
%		Generate children of $n$\;
		\For{$n$의 각 새끼 마디 $n'$}{
			\If{$L < v_{\mathcal{I}}[n']$}{
				$L \gets v_{\mathcal{I}}[n']$\;
				$\mathcal{X}$을 $n'$에 대응하는 $\mathcal{I}$-집합으로 수정\;
			}
			\lIf{$v_{\mathrm{LP}}^*[n] > L$이고 $n'$이 잎 마디 아님}{$\mathfrak{T}$에 $n'$을 추가}
		}
		\For{$n'' \in \mathfrak{T}$} {
			\lIf{$L >  v_{\mathrm{LP}}^*[n'']$}{$\mathfrak{T}$에서 $n''$을 제거}
		}
	}
}
\end{algorithm}
} \fi

@@

\ifen {
\begin{algorithm}[h] 
%\DontPrintSemicolon
\caption{Dynamic program for Ellis's problem with integral application costs.} \label{ellisDP1}
\KwIn{Utility values $t \in(0, \infty)^m$, admissions probabilities $f \in (0, 1]^m$, application costs $g \in \mathbb{N}^m$, budget $H \in\mathbb{N}$.}
Index schools in ascending order by $t$\;
%\SetKwProg{Fn}{function}{ do}{end}
%\Fn{$V(j, h)$}{
%	\lIf{$h < g_j$}{\Return{$-\infty$}}
%	\lElseIf{$j = 0$ or $h=0$}{\Return{$0$}}
%	\lElse{\Return{$\max\bigl\{ V(j-1, h), (1 - f_j) V(j-1, h-g_j) + f_j t_j \bigr\}$}}
%}
Fill a lookup table with the values of $V[j, h]$\; \label{Vcreatedlookuptable}
$h \gets H$\;
$\mathcal{X} \gets \O$\;
\For{$j = m, m-1, \dots, 1$}{
	\If{$V[j-1, h] < V[j, h]$}{
		$\mathcal{X} \gets \mathcal{X}\cup\{j\}$\; 
		$h \gets h - g_j$\;
	}
}
\Return{$\mathcal{X}$}
\end{algorithm}
} \else {
\begin{algorithm}[h] 
%\DontPrintSemicolon
\caption{정수 지원 비용의 엘리스 문제를 위한 동적 계획 해법.} \label{ellisDP1}
\KwIn{효용 모수 $t \in(0, \infty)^m$, 합격 확률 $f \in (0, 1]^m$, 지원 비용 $g \in \mathbb{N}^m$, 예산 $H \in\mathbb{N}$.}
$t$의 순서대로 학교를 배열한다\;
%\SetKwProg{Fn}{function}{ do}{end}
%\Fn{$V(j, h)$}{
%	\lIf{$h < g_j$}{\Return{$-\infty$}}
%	\lElseIf{$j = 0$ or $h=0$}{\Return{$0$}}
%	\lElse{\Return{$\max\bigl\{ V(j-1, h), (1 - f_j) V(j-1, h-g_j) + f_j t_j \bigr\}$}}
%}
$V[j, h]$의 값으로 표를 채운다\; \label{Vcreatedlookuptable}
$h \gets H$\;
$\mathcal{X} \gets \O$\;
\For{$j = m, m-1, \dots, 1$}{
	\If{$V[j-1, h] < V[j, h]$}{
		$\mathcal{X} \gets \mathcal{X}\cup\{j\}$\; 
		$h \gets h - g_j$\;
	}
}
\Return{$\mathcal{X}$}
\end{algorithm}
}\fi

@@

\ifen \subsection{Simulated annealing heuristic} \else \subsection{모의 담금질 휴리스틱}\fi\label{numericalexperiments}
\ifen
Simulated annealing is a popular local-search heuristic for nonconvex optimization problems. Because of their inherent randomness, simulated-annealing algorithms offer no accuracy guarantee; however, they are easy to implement, computationally inexpensive, and often produce solutions with a small optimality gap. In this section, we present a simulated-annealing algorithm for Ellis's problem. It is based on the procedure for integer programs outlined by Wolsey (1998, \S\,12.3.2).
\else
모의 담금질은 비볼록 최적화 문제를 위한 인기 많은 지역 탐색 휴리스틱이다. 선천적인 확률성 때문에 모의 담금질 해법에는 보장된 정확도가 없다. 반면에 구현하기 쉽고 계산 비용이 작으면서 최적에 가까운 해를 구하는 경향이 있다. 본 항에서, 엘리스의 문제를 위한 모의 담금질 해법을 제시한다. Wolsey (1998, \S\,12.3.2)가 제시한 정수 계획 모의 담금질 해법이 바탕이 된다.
\fi
